---
title: "Assignment 12"
author: "Yatish"
date: "December 1, 2015"
output: html_document
---

Neo4j community edition can be downloaded from the official site directly. [neo4j](http://neo4j.com/download/other-releases/)

#### Installation

Neo4J installation is very simple with only one prerequisite i.e. [OpenJDK7](http://openjdk.java.net/)

Once you have this Java version you can directly go inside the neo4j unzipped folder and within it bin folder and type the following command to run the server:

`
cd Downloads/neo4j-community-2.2.4/bin

neo4j start
`
The first time you open this browser you are allowed to set a new password for this server by clicking on the password link on the left pane. The default username is neo4j and the default password is neo4j.

##### Installing neo4j in R
`install.packages("devtools")
install.packages("httr")
devtools::install_github("nicolewhite/RNeo4j")`

```{r}
library(RNeo4j)
```

```{r}
graph = startGraph("http://localhost:7474/db/data/",username="neo4j",password="yatish")
#clear(graph)
```


```{r}
#creating nodes
#createNode(graph object, label, key1=value1, key2=value2)
ben <- createNode(graph, "Person", name="Ben", age=45, designation="Sr. Manager")
mel <- createNode(graph, "Person", name="Mel", age=38, designation="Team Leader")
kelly <- createNode(graph, "Person", name="Kelly", age=30, designation="Programmer")
mike <- createNode(graph, "Person", name="Mike",age=27, designation="Software Tester")
john <- createNode(graph, "Person", name="John", age=28, designation="Android developer")
ella <- createNode(graph, "Person", name="Ella", age=28, designation="Marketing")
dave <- createNode(graph, "Person", name="Dave", age=48, designation="Zonal Head")
maggi <- createNode(graph, "Person",name="Maggi", age=28, designation="Assistant")
laugh<- createNode(graph, "Club",name="XYZ laughter club", motto="learn to laugh",members=50)
sports <- createNode(graph,"Sports",name="Cricket",host="ICC")


# Creating relationships
r1 <- createRel(mel,"WORKS_FOR",ben)
r2 <- createRel(kelly,"WORKS_FOR",ben)
r3 <- createRel(mike,"WORKS_FOR",ben)
r4 <- createRel(john,"WORKS_FOR",ben)
r5 <- createRel(ella,"WORKS_FOR",ben)
r6 <- createRel(ben,"WORKS_FOR",dave)
r7 <- createRel(maggi, "WORKS_FOR",dave)
r8 <- createRel(maggi, "FRIENDS_WITH",ella)
r9 <- createRel(ella, "FRIENDS_WITH",maggi)
r10 <- createRel(john, "FRIENDS_WITH",mike)
r11 <- createRel(mike, "FRIENDS_WITH",john)
r12 <- createRel(dave, "PART_OF",laugh)
r13 <- createRel(john,"PART_OF",laugh)
r14 <- createRel(mike,"PART_OF",laugh)
r15 <- createRel(dave,"LIKES",sports)
r16 <- createRel(ben,"LIKES",sports)
r17 <- createRel(mike,"LIKES",sports)
r18 <- createRel(dave,"KNOWS",ella)
```

##Visualisation

```{r}
library(igraph)

query="
MATCH (n) -->(m)
RETURN n.name,m.name
"
cypher(graph, query)
edgelist = cypher(graph, query)
ig = graph.data.frame(edgelist, directed=F)

betweenness(ig)
closeness(ig)
plot(ig)
```


### Queries

```{r}
# Query to display all the employees who works for somebody
query = "
MATCH (m:Person)-[:WORKS_FOR]->(works_for:Person)
WHERE m.age={age}
RETURN m.name,m.age,m.designation,works_for.name
"

cypher(graph, query,age=28)

query = "
MATCH (m:Person)-[:WORKS_FOR]->(w:Person),
(w:Person)-[:PART_OF]->(laugh)
RETURN m.name,m.age,m.designation,laugh.name,w.name
"

cypher(graph, query)


query = "
MATCH (m:Person)-[:WORKS_FOR]->(w:Person)
Where w.name= {name}
RETURN w, Collect(m.name) AS employees
"
cypherToList(graph, query,name="Dave")
```


Query to find the shortest path between two nodes
```{r}
query = "
MATCH p = shortestPath((kelly:Person)-[:WORKS_FOR*]->(dave:Person))
WHERE kelly.name = 'Kelly' AND dave.name = 'Dave'
RETURN p
"

p = cypherToList(graph, query)[[1]]
p$p$length
```

