---
title: "Twitter API and data analysis"
author: "Yatish"
date: "November 10, 2015"
output: html_document
---



```{r}
library(RCurl)                                                                                             
library(ROAuth)                                                                                               
library(streamR)                                                                                            
library(twitteR)
library(base64enc)
library(httr)
                                                                                              
download.file(url="http://curl.haxx.se/ca/cacert.pem", destfile="cacert.pem")                                   
                                                                        
                                                                       
# Twitter configuration                                                                                         
requestURL              <- "https://api.twitter.com/oauth/request_token"                                              
accessURL               <- "https://api.twitter.com/oauth/access_token"                                               
authURL                 <- "https://api.twitter.com/oauth/authorize"                                                  
consumerKey         <- "Nkbu60VFyVijths7N5gejwpBc"                                                                                   
consumerSecret      <- "jfYKTw8RV0r4T7BAKihPEdpuntC4IOLqfkZ87emUVrMdPBUCGV"                                                                                   
oauth_token             <- "125868872-NTLHWjNpOB80Jr3GX9usDE88jfooFiSjcffuW4AW"                                                                                      
oauth_token_secret  <- "8TSRFxE12Mu2KSHlD1aqCuCNkNIiLOcGER5OV5rUOAeeY"                                                                                    
my_oauth <- OAuthFactory$new(   consumerKey=consumerKey,
                                consumerSecret=consumerSecret, 
                                requestURL=requestURL,
                                accessURL=accessURL, authURL=authURL)                                           
my_oauth$handshake(cainfo="cacert.pem")   

##Once executing the above code returns true.                                                                        
##You will be given a link to authorize your application to get twitter feeds.                                     
##Copy the link in your browser. Click on Authorize MyApplication. You will receive a pin number.                     
##Copy the pin number and paste it in the console.                                                                  
##Once your application has been authorized you need to register your credentials.                                  


#registerTwitterOAuth(my_oauth)
setup_twitter_oauth(consumerKey, consumerSecret, oauth_token, oauth_token_secret)

# Press 1 to allow the file to access the credentials 

##Now start reading tweets
some_tweets = searchTwitter("starbucks", n=1500, lang="en")

# get the text
some_txt = sapply(some_tweets, function(x) x$getText())
head(some_txt)
```


`install.packages("sentiment")`
```{r}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(devtools, installr)
install.Rtools()
install_url("http://cran.r-project.org/src/contrib/Archive/Rstem/Rstem_0.4-1.tar.gz")
install_url("http://cran.r-project.org/src/contrib/Archive/sentiment/sentiment_0.2.tar.gz")



# remove retweet entities
some_txt = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", some_txt)
# remove at people
some_txt = gsub("@\\w+", "", some_txt)
# remove punctuation
some_txt = gsub("[[:punct:]]", "", some_txt)
# remove numbers
some_txt = gsub("[[:digit:]]", "", some_txt)
# remove html links
some_txt = gsub("http\\w+", "", some_txt)
# remove unnecessary spaces
some_txt = gsub("[ \t]{2,}", "", some_txt)
some_txt = gsub("^\\s+|\\s+$", "", some_txt)
 
# define "tolower error handling" function
try.error = function(x)
{
# create missing value
y = NA
# tryCatch error
try_error = tryCatch(tolower(x), error=function(e) e)
# if not an error
if (!inherits(try_error, "error"))
y = tolower(x)
# result
return(y)
}
# lower case using try.error with sapply
some_txt = sapply(some_txt, try.error)
 
# remove NAs in some_txt
some_txt = some_txt[!is.na(some_txt)]
names(some_txt) = NULL



class_emo = classify_emotion(some_txt, algorithm="bayes", prior=1.0)
# get emotion best fit
emotion = class_emo[,7]
# substitute NA's by "unknown"
emotion[is.na(emotion)] = "unknown"

# classify polarity
class_pol = classify_polarity(some_txt, algorithm="bayes")
# get polarity best fit
polarity = class_pol[,4]
# Create data frame with the results and obtain some general statistics
# data frame with results
sent_df = data.frame(text=some_txt, emotion=emotion,
polarity=polarity, stringsAsFactors=FALSE)
 
# sort data frame
sent_df = within(sent_df,
emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))



# Let’s do some plots of the obtained results
# plot distribution of emotions
ggplot(sent_df, aes(x=emotion)) +
geom_bar(aes(y=..count.., fill=emotion)) +
scale_fill_brewer(palette="Dark2") +
labs(x="emotion categories", y="number of tweets") +
ggtitle("Sentiment Analysis of Tweets about Starbucks\n(classification by emotion)") +
theme(plot.title = element_text(size=12, face="bold"))


# plot distribution of polarity
ggplot(sent_df, aes(x=polarity)) +
geom_bar(aes(y=..count.., fill=polarity)) +
scale_fill_brewer(palette="RdGy") +
labs(x="polarity categories", y="number of tweets") +
ggtitle("Sentiment Analysis of Tweets about Starbucks\n(classification by polarity)") +
theme(plot.title = element_text(size=12, face="bold"))



# Separate the text by emotions and visualize the words with a comparison cloud
# separating text by emotion
emos = levels(factor(sent_df$emotion))
nemo = length(emos)
emo.docs = rep("", nemo)
for (i in 1:nemo)
{
tmp = some_txt[emotion == emos[i]]
emo.docs[i] = paste(tmp, collapse=" ")
}
 
# remove stopwords
emo.docs = removeWords(emo.docs, stopwords("english"))
# create corpus
corpus = Corpus(VectorSource(emo.docs))
tdm = TermDocumentMatrix(corpus)
tdm = as.matrix(tdm)
colnames(tdm) = emos
 
# comparison word cloud
comparison.cloud(tdm, colors = brewer.pal(nemo, "Dark2"),
scale = c(3,.5), random.order = FALSE, title.size = 1.5)
 